Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-20 article.tex
Suppression d'une phrase de liaison inutile

\subsection{Density-based clustering methods}
Although the filtering methods are providing good results, it is still not enough.
Therefore, we will modify those criteria to take in account the variations of \acrshort{bs} density. Thus, we need some measurement of this density.

As those problems are equivalent and because this is simpler to visualise, we will say that we are looking for detecting the cities.
\subsubsection{\acrshort{dbscan}}
\acrshort{dbscan} consists in detecting clusters based on the density of points, using two parameters:
\begin{itemize}
    \item \emph{$\varepsilon$}: A distance threshold under which two points are considered close enough to be considered neighbours;   
    \item \emph{$n_{\text{min}}$}: The shortest number of neigbours a points needs to have to be considered as a core point of a cluster.
\end{itemize}

@@

\section{Finding the real neighbours}
\noindent Each of the precedent methods gives us a list of potential neighbours for each \acrshort{bs}. However, we know that some of this neighbouring connexions are wrong,
either because of the neighboring graph construction method or physical specificities linked to the base stations themselves.

>>>>

\subsection{Density-based clustering methods}
\subsubsection{\acrshort{dbscan}}
\acrshort{dbscan} consists in detecting clusters based on the density of points, using two parameters:
\begin{itemize}
    \item \emph{$\varepsilon$}: A distance threshold under which two points are considered close enough to be considered neighbours;   
    \item \emph{$n_{\text{min}}$}: The shortest number of neigbours a points needs to have to be considered as a core point of a cluster.
\end{itemize}

@@

\section{Contributions}
\noindent Each of the precedent methods gives us a list of potential neighbours for each \acrshort{bs}.
However, we know that some of this neighbouring connexions are wrong,
either because of the neighboring graph construction method or physical specificities linked to the base stations themselves.
